\documentclass[12pt,french,english,notitlepage]{report} % main lang last
%\documentclass[12pt,english, spanish, french]{thesis}
%
% usage notes: 
% - Place figures in the /fig folder
% - Place chapters in the /chapters folder.
% - References should be included in ./mybib.bib


% Some page styling:
%\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm]{geometry}
\usepackage[margin=0.7in]{geometry}
%\usepackage{fancyhdr}
%\pagestyle{fancy}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
% Interlineado
%\usepackage{setspace}
%\setstretch{1.5}

% Bibtex
%\usepackage{cite} % use cite with natbib but not with biblatex
%\usepackage{natbib}
\usepackage[style=numeric,backend=bibtex]{biblatex}
\bibliography{refs} % put here in preamble when using biblatex

\usepackage[titletoc]{appendix}
\usepackage{float}
\usepackage{graphicx}
\usepackage{rotating}
%\usepackage{eso-pic}
%\usepackage{multicol}
\usepackage{enumerate} % custom lists
%\usepackage{url}
%\usepackage{soul}
% for working with eps
\usepackage{epstopdf} 
\usepackage{color} % color text
\usepackage{titlesec} % to change the way \paragraph formats the titles
\usepackage{textcomp} % for copyright symbol
\usepackage{quotchap} % for chapter openning quotes
\usepackage{titling}
\usepackage{tablefootnote}

% Define a path for the fig folder
% nota: imges must be in the same folder or subfolders of this file, if not pdf2latex will complain
% ---------------------- %
\newcommand{\figpath}{./fig}
%\graphicspath{ {./fig/} }

% Bibligraphy path
% ---------------------- %
\newcommand{\bibpath}{.}

\usepackage[hidelinks]{hyperref}

% ---------------------- %
% Title
% ---------------------- %
\title{The Legacy Project}
\author{
  Michel, Nicolas\\
  \texttt{nicolas@legacy.network}
  \and
  Almonacid, Vicente\\
  \texttt{vicente@legacy.network}
}
\date{\today\\v0.7.2} % v0.7.1 hasn't been commited yet

% end preamble
%

% Start content
% -------------------------------------------------------------------------------------- %
\begin{document}

% \begin{titlingpage}
%     \maketitle
%     \begin{abstract}
%         Legacy is a blockchain-based application that allows people to easily distribute assets upon their dead (or, in general, upon any verifiable event).
%     \end{abstract}
% \end{titlingpage}

\maketitle
\begin{abstract}
    Legacy is a blockchain-based application allowing people to easily distribute assets upon their death or upon any set of verifiable events.
    The application integrates a variety of services that will be developed progressively as blockchain technology consolidates. 
    This paper mainly describes Legacy's initial releases, which allow the transfer of digital assets, such as images, videos and text documents. 
    The application's core functionalities will be initially developed on the Ethereum blockchain. These include a Proof of Life engine responsible for determining whether the user is alive or not, and a smart contract that manages user assets and schedules their distribution according to a given set of triggering events.
    Leveraging the unique characteristics of blockchain platforms, Legacy is designed to ensure security, reliability and long-term availability. 
    Typical use cases include transfer of sensitive data (\textit{e.g.}, personal meaningful information), cryptocurrency holdings and confidential data such as online service credentials.
    In the long-term, Legacy expects to integrate smart property and other blockchain-based digital assets, as well as to provide a platform for peer-to-peer legal and technical assistance, thus becoming a next-generation smart-will solution.

\end{abstract}

% acknowledgements
\chapter*{}
\include{chapters/acks}

\include{chapters/disclaimer}

\tableofcontents

% \listoffigures

% ---------------------- %
% Main Content
% ---------------------- %

\include{chapters/exec_summ}
%\include{chapters/business_model}
\include{chapters/implementation}
\include{chapters/architecture}
\include{chapters/token}
%\include{chapters/roadmap}
\include{chapters/legal}
%\include{chapters/crowdfunding}
%\include{chapters/team}

% ---------------------- %
% Appendix
% ---------------------- %
%\include{chapters/appendix}

% ---------------------- %
% Bibliography
% ---------------------- %
%
% 1. using natbib
%\bibliographystyle{plain}
%\bibliography{\bibpath/refs}
%
% 2. uing biblatex
\printbibliography

\end{document}}
