\chapter*{GENERAL DISCLAIMER} % (fold)
\label{cha:general_disclaimer}


\textbf{The White Paper shall be read together with the T\&C and does not constitute an offer or an invitation to sell shares, securities or rights belonging to Legacy.}
\vspace{2mm}

Legacy is not deemed providing any information which can be considered as a basis for an investment decision.
\vspace{2mm}

Legacy is not providing any investment recommendation nor investment advice.
\vspace{2mm}

The White Paper including the T\&C does not constitute or form part of, and should not be construed as, an offer for a sale or subscription, or an invitation to buy or subscribe securities or financial instruments. It does not constitute the basis for, or should not be used as a basis for, or in connection with, a contract for the sale of securities or financial instruments or a commitment to sell securities or financial instruments of any kind.
\vspace{2mm}

Legacy expressly disclaims any liability for any direct or indirect loss or damage of any kind arising directly or indirectly from:
\begin{enumerate}[i.]
	\item any reliance on the information contained in this document,
	\item any error, omission or inaccuracy in said information, or
	\item any resulting action that may be brought.
\end{enumerate}


\subsubsection*{Regulatory Uncertainties of Tokens} % (fold)
\label{ssub:regulatory_uncertainties_of_tokens}
The regulatory status of tokens and distributed ledger technology is unclear. It is difficult to predict how or whether regulatory authorities may apply existing regulation with respect to such technology and tokens platform. It is difficult to predict how or whether the regulator may implement changes to the law and regulation affecting distributed ledger technology and its applications, including the LEG Tokens and the platform. Regulatory actions could negatively impact the platform in various ways, including, for purposes of illustration only, though a determination that the purchases, sale and delivery of the LEG Tokens constitutes unlawful activity or that LEG Tokens is a regulated instrument that requires registration of the platform itself, or the licensing of some or all of the parties involved in the purchase, sale and delivery thereof. The platform may cease operations in a jurisdiction in the event where that regulatory actions, or changes to low or regulation, make it illegal to operate in such jurisdiction, or commercially undesirable to obtain the necessary regulatory approval(s) to operate in such jurisdiction.
% subsubsection regulatory_uncertainties_of_tokens (end)


\paragraph{A LEG Token  is not a financial instrument.} A LEG Token does not represent an investment in a security or a financial instrument within the meaning of EU Directive 2014/65/EU of the European Parliament and of the Council of 15 May 2014 relating to markets in financial instruments: the LEG Token confers no direct or indirect right to the Legacy's capital or income, nor does it confer any governance right within Legacy.


\paragraph{A LEG Token is not proof of ownership or a right of control.} It does not confer any right on any asset or share in Legacy. A LEG Token does not grant any right to participate in control over Legacy's management or decision-making set-up.

% \paragraph{A LEG Token is not an electronic currency} within the meaning of EU Directive 2009/110/EC of the European Parliament and of the Council of 16 September 2009 relating to access to and pursuit of the business of electronic currency institutions: LEG Tokens are not accepted outside the platform and a LEG Token does not have a fixed exchange value equal to the amount delivered at the time of its issue.
\vspace{4mm}
\noindent
\textbf{A LEG Token is not an electronic currency} within the meaning of EU Directive 2009/110/EC of the European Parliament and of the Council of 16 September 2009 relating to access to and pursuit of the business of electronic currency institutions: LEG Tokens are not accepted outside the platform and a LEG Token does not have a fixed exchange value equal to the amount delivered at the time of its issue.

\vspace{4mm}
\noindent
\textbf{A LEG Token does not qualify as a payment service} within the meaning of EU Directive (2007/64/EC) of 13 November 2007 relating to payment services in the internal market, nor within the meaning of the (EU) Directive relating to payment services 2 (DSP 2) N° 2015/2366 of the European Parliament and of the Council of 25 November 2015: the ICO does not involve the purchase/sale of LEG Token and the Legacy’s business does not consist in receiving currencies against the delivery of LEG tokens; as such, a LEG Token is not a means of payment either.

\paragraph{A LEG Token is a cryptographic token used by the platform.}
A LEG Token is a crypto-currency, i.e. an unregulated, digital asset, issued and controlled by its developers, and used and accepted only by the members of a given community.

\paragraph{Intellectual property belonging to Legacy.}
The User acknowledges that Legacy retains sole and exclusive ownership of all intellectual, industrial and expertise rights relating to the LEG Tokens, documents, data, etc. The technical and technological resources and expertise used to design both LEG Tokens, and documents of any nature, shall remain the exclusive property of Legacy regardless of whether they are protected under an intellectual property clause. Therefore, any document, listing, database, etc., in its entirety, is given to the User in return for payment or free of charge solely as a loan for use that exclusively enables them to use the platform, under or not a separate availability and/or non-disclosure agreement that forms an integral part of these T\&C, and may not be used by the User for any other purpose without incurring their liability 

\paragraph{Protection of Personal Data.} The processing of personal data performed under the platform will be declared in France to the National Commission for Data Protection and Liberties. In accordance with Article 32 of French law N° 78-17 of 6 January 1978 relating to Information Technology, Files and Civil Liberties, Legacy, which is responsible for processing the said data, will inform the User that it is processing their personal data. The details entered by the User on the forms available on the website are intended for authorized Legacy personnel for administrative and business management purposes. These data are processed to allow Users to access and use the services under the platform.

\begin{itemize}
	\item The User is entitled to access, question, modify, rectify and delete their own personal data,
	\item the User is also entitled to object to the processing of their personal data for legitimate reasons, as well as to object to the use of such data for the purposes of prospecting activities.
\end{itemize}

To exercise their rights, the User shall notify their request to Legacy, attaching a copy of their signed ID document.
\vspace{2mm}.
The User shall comply with the provisions of French law N° 78-17 of 6 January 1978 relating to Information Technology, Files and Civil Liberties, amended, any breach of which is deemed a criminal offence. In particular, they shall not collect or misuse data and, in general, perform any act likely to infringe the privacy or reputation of individuals

\paragraph{Regulatory uncertainties.}
The User acknowledges and accepts that the ICO launched by the Legacy is taking place within a French legal environment that is still under development. New laws or rules may subsequently frame, modify or clarify the practice of such ICO. Where necessary, should legislative changes conflict with all or part of these terms and conditions, Legacy reserves the right to amend the terms of the ICO as appropriate, retroactively if necessary, in order to ensure that the ICO remains legal and compliant with the various French regulatory bodies.

\vspace{2mm}
Legacy will respond to any request issued via regular legal process aimed at obtaining specific information about the Users, particularly in terms of the fight against money laundering.

\paragraph{Applicable law and jurisdiction.}
These T\&C and any contract relationship relating to the services offered by Legacy are governed exclusively by French law, the Legacy's commitment being subject to this clause. Translations of the White Paper including the T\&C herein, made available to the User, are purely informative and are not legally binding. The French version of these terms and conditions has sole legal force. If an English version is provided to Users, it is for information purpose only.
Legacy and the Users agree to seek an amicable settlement prior to bringing any legal action. Failing this, any dispute, of any nature whatsoever, will be brought expressly before the court with jurisdiction over the Legacy's registered headquarters, as no document can affect a novation or waiver of this jurisdiction clause.

% chapter general_disclaimer (end)