\chapter{Legal Considerations} % (fold)
\label{cha:legal_considerations}

\textit{[work in progress]}

\vspace{4mm}

It is clear that Legacy may involve several legal issues, among which we may mention:

\begin{itemize}
	\item Legally binding smart contracts according to each local jurisdiction, wherein Legacy expects to operate. The process of transferring assets through smart contracts must strictly comply with local regulations in order to be legally valid.
	\item Conflict resolution in cases where the smart contract alone executes unexpectedly.
	\item Legal disagreements in cases where testators and beneficiaries belong to different countries or jurisdictions.
	\item Ensuring that Legacy's smart contract is in fact the \textit{last} will created by the testator, which otherwise would invalidate the contract in some jurisdictions.
	\item Taxation of estates: wills created and executed through Legacy may also be subject to taxes under certain jurisdictions. Those cases must be clearly identified in order to avoid tax evasion.
\end{itemize}


% ---------------------------------------------------------------------------------------------------------------- %
% Foundation
% ---------------------------------------------------------------------------------------------------------------- %
\section{The Legacy Foundation} % (fold)
\label{sec:the_legacy_foundation}

There are several scenarios in which software alone cannot provide fully satisfactory solutions and therefore some arbitrage mechanism is required.
On the other hand, finding people to deliver assets entrusted to Legacy may prove difficult. Beneficiaries may move, change their phone numbers, email addresses, etc.
In order to handle these cases, a separate, non-profit entity will be created: The Legacy Foundation. This entity will be completely autonomous and independent from the Legacy Organization.

In order to ensure correct operation, the Legacy Foundation will receive a percentage of the service operation fees, which will be automatically transferred from user smart contracts once the service is paid. In addition, a percentage of the funds obtained during the crowdsale will be also allocated to The Foundation.

In the long term, besides playing its mediator role, the Foundation will also intervene to encourage constant platform development (\textit{e.g.}, by proposing bounty programs) and will assist in major software upgrades.
At this stage, the structure as well as the policies adopted by The Foundation will be decided by the community following a decentralized governance system.

Other functions envisaged for The Foundation include: 
taking care of correctly transmitting user assets when automated means fail and monitoring the Legislative process of transmitting properties.
%taking care of correctly transmitting user assets if and only if purely automated means fail, and monitoring changes in the legislative process of transmitting properties.
Finally, the foundation may also run storage nodes to improve redundancy and service reliability.

% section the_legacy_foundation (end)

% chapter legal_consideration (end)